%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Sam Odle} % Your name
\address{703.887.6899 \\ sro27@cornell.edu \\ Washington DC, 20002} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Lead Technologist}{2018 - Present}{Booz Allen Hamilton}{Washington, DC}
\item Digital Strategist in Booz Allen's Strategic Innovation Group leading the execution of digital product development and digital transformation projects.  Continually facilitating  in–person  and  virtual  meetings  with  clients  to  design  and  deploy products and  organizational  strategic components.
\item Product owner for multiple applications deployed by the client's OCIO.  Recently lead 5 person agile team through discovery, design, and MVP development of low code application.
\item Collaborate with stakeholders to understand requirements and liason with internal cross-functional teams to deliver both agency wide and solution specific modernization roadmaps.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Co-Founder}{2019 - Present}{Fork, Inc}{ Remote / Boston, MA}
\item As CTO, responsible for product strategy, technical recruiting, and MVP development. Fork's AI discovers career pathways that optimize the placement and growth of talent. Fork was a TechStars finalist and has incubated out of the Harvard Innovation Lab since Summer 2020.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Program Manager}{2016 - 2018}{Simulation Dynamics}{Knoxville, TN}
\item Owned program efforts for global supply chain optimization and manufacturing process reliability projects. Identified new growth areas for machine intelligence, developed product and project roadmaps, and monitored implementation schedule and cost.  
\item Managed agile project teams of 3-6 people to develop and deploy solutions to over 160 sites; responsible for project oversight and strategy, task delegation, and final deliverables.

\end{rSubsection}

\begin{rSubsection}{Business Leader}{2013 - 2016}{Procter \& Gamble}{Greensboro, NC}
\item Responsible for all day to day start-up and product qualification activities for line 4 as part of P\&G's \$100M skin care Greensboro expansion.  Delivered on-time qualifications of every line 4 SKU.
\item Managed 4 teams of line technicians and 2 teams of electrical and instrumentation technicians.  Successfully hit all start-up reliability targets.  Received CEO award as top site performer.
\item Promoted from Process Engineer in July 2014.  As Process Engineer, developed the algorithms and user interfaces for an app that simplified loss analysis. Led roll-out to over 60 sites in 15 countries.

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education \& Certifications}

{\bf Bachelor of Science} \hfill {\em May 2013} \\ 
Cornell University, Electrical Engineering \\

{\bf Master of Science} \hfill {\em Expected 2022} \\ 
George Washington University, Computer Science
\begin{center}
\rule{0.1\textwidth}{.05pt}
\end{center}
%{\bf George Washington University} \hfill {\em est. Fall 2022} \\ 
%M.S. Candidate, Computer Science
\begin{tabular}{ @{} >{}l @{\hspace{6ex}} l }
Pragmatic Certified Product Manager (2021) & Startup School, Y Combinator (2020)  \\
AWS Cloud Practitioner, AWS (2021) & Scrum Master, Scrum Alliance (2020) \\
Project Management Professional, PMI (2019) & ITIL Service Operation, Axelos (2019) \\
Design Thinking, UVA Darden (2019)
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Skills \& Certifications}

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Computer Languages & Prolog, Haskell, AWK, Erlang, Scheme, ML \\
%5Protocols \& APIs & XML, JSON, SOAP, REST \\
%Databases & MySQL, PostgreSQL, Microsoft SQL \\
%Tools & SVN, Vim, Emacs
%\end{tabular}

%\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
